State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
editing in LS for the zero input

by substituting \ref{eq:Reducednoiseterm} and \ref{eq:QMatrix} in \ref{eq:ReducedForm} with zero input and using $\xi = 1-\zeta T_s$ at each time instant we can write

>>>>

by substituting \ref{eq:Reducednoiseterm} and \ref{eq:QMatrix} in \ref{eq:ReducedForm} and using $\xi = 1-\zeta T_s$ at each time instant we can write
